%-------------------------
% Resume in Latex
% Author : Alex Ryndin
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1:}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeBigItem}[2]{
  \item{
    \textbf{#1:}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item{
    \begin{tabular}[t]{l r}
    	\textbf{#1} \\
	{#2}, \textit{\small#4} \\
	 \textit{\small #3} 
    \end{tabular}\vspace{-5pt}
  }
}

\newcommand{\expSubheading}[4]{
\vspace{-1pt}\item{
    \begin{tabular}[t]{l  l}
    	\textbf{#1}, { #3} \\
	 \textit{#2 }\textbar \textit{ \small #4} 
    \end{tabular}\vspace{-5pt}
  }
}

\newcommand{\educationSubheading}[4]{
\vspace{-4pt}\item{
    \begin{tabular}[t]{l r}
    	\textbf{#1} \\
	{#2}, \textit{\small#4} \\
	 \textit{\small #3} 
    \end{tabular}\vspace{-5pt}
  }
}

\newcommand{\resumeSubItem}[2]{\vspace{-0pt}\resumeItem{#1}{#2}\vspace{-0pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://alexryndin.me/}{\Large Alex Ryndin}} & Email : \href{mailto:trytohire@alexryndin.me}{trytohire@alexryndin.me}\\
  \href{http://alexryndin.me/}{http://www.alexryndin.me} & Mobile : +7-999-700-17-13 \\
\end{tabular*}

\begin{minipage}[t]{0.66\textwidth} 
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {National University of Science and Technology MISiS}{Moscow, Russia}
      {Bachelor of Information Systems and Technologies;  GPA: 4.95 }{Sep. 2012 -- June. 2016}
    \educationSubheading
      {National University of Science and Technology MISiS}{Moscow, Russia}
      {Master of Information Systems and Technologies;  GPA: 4.7 }{Sep. 2016 -- June. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \expSubheading
      {Mail.ru Group}{Moscow, Russia}
      {DevOps Developer}{July 2019 - Present}
      \resumeItemListStart
      \resumeItem{Internal Authorization Management System}
        {Played a huge part in internal authorization management system design and implementation. This modular and highly extendable system allowed for centralized user authorization management over more than ten different services, and systems like DBMS, Dashboards, Notebooks, various platforms, and services. Technology stack included Clickhouse, Python (aiohttp), Kerberos, Nginx}
      \resumeItem{Internal Hadoop Distribution Development}
        {Build, tested and prepared for installation internal Cloudera-like Hadoop distribution based on Apache Hadoop artifacts using fpm}
        \resumeItem{Hardware Cluster Support and Maintenance}
        {Upgraded internal metrics system to a new technology stack. Created a number of software modules provided logs and metrics parsing, transferring, receiving and injestion. Provided support and maintenance for a cluster with more than 400 nodes. Upgraded with zero downtime high load (over 20MB/s per node) 6 nodes Apache Kafka Cluster. Upgraded to the last version a number of Clickhouse clusters. Played a huge part in Hadoop cluster upgrade (over 350 nodes).  Technology stack included Clickhouse, Apache Hadoop, PostgreSQL, Mysql, Prometeus, Graphite, GitLab}
      \resumeItemListEnd
    \expSubheading
      {Arenadata}{Moscow, Russia}
      {Software Engineer}{May 2017 - June 2019}
      \resumeItemListStart
        \resumeItem{Arenadata Grid}
          {A totally new product based on Apache Ignite was introduced to the Arenadata Enterpise Platform. Being head of development, I made the integration of the product, performed load testing, created automatic deployment scripts}
        \resumeItem{Arenadata Cluster Manager}
          {Two new services were added to the brand new Arenadata Cluster Manager. A lot of Ansible scripts has been developed. Made integration with metrics system based on Graphite/Graphana}
        \resumeItem{Arenadata Hadoop}
          {Installation and maintenance, support and troubleshooting}
        \resumeItem{Arenadata Ambari}
          {Python deployment scripts development and refactoring. A new product has been integrated as a part of Arenadata Hadoop stack - Hive LLAP. Over 100 commits in Arenadata Ambari repo}
      \resumeItemListEnd

    \expSubheading
      {Aria Invertor}{Stary Oskol, Belgorod Oblast, Russia}
      {Software Developer}{Mar 2016 - Jun 2016}
      \resumeItemListStart
        \resumeItem{Task Management System}
          {Designed and developed a kind of web-oriented ERP System from scratch, written in Python with Flask, backed with mysql and SQLAlchemy on a storage level. System was developed to facilitate a process of creating, assigning and monitoring of work tasks.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

 %-----------PUBLICATIONS & ACHIEVEMENTS------------
\section{Publications \& Achievements}
  \resumeSubHeadingListStart
     \resumeSubItem{Samsung Compiler Bootcamp}
        {Accomplished introductory course on compilers development}
     \resumeSubItem{RedF programming language}
        {Implemeted lisp-like programming language in C \href{https://github.com/ValBaturin/redF}{https://github.com/ValBaturin/redF}; Live preview - \href{http://projectf.alexryndin.me/}{http://projectf.alexryndin.me/}}
    \resumeSubItem{"Memorable" Computing (rus)}
        {Introduction to a concept and principles of new Arenadata In-Memory computing platform called Arenadata Grid. Open Systems Journal (ISSN 1028-7493), June 2018.}
  \resumeSubHeadingListEnd


\end{minipage}
\begin{minipage}[t]{0.33\textwidth} 

%-----------SKILLS------------
\section{Skills}
\begin{itemize}[leftmargin=*]
	\item{ \textbf{Languages}{\vspace{-8pt}}
		 \begin{itemize}
			 \item{Go, Python}
			 \item{Java}
			 \item{C, Rust}
		\end{itemize}
    }
	\item{ \textbf{Tools}{\vspace{-8pt}}
		 \begin{itemize}
			 \item{\textit{\small{Can't live without:}}\newline}
			Linux (esp. Arch), vim, bash, zsh;
			  \item{\textit{\small{Use a lot:}}\newline}
			Puppet, Ansible, Jira, Git and GitLab;
			 \item{\textit{\small{Familiar:}}\newline}
			 Haskell :), TeX,  Google Cloud Platform
		\end{itemize}

    }
	\item{ \textbf{Technologies:}{\vspace{-0pt}}\newline
	    Prometheus, Grafana, Sentry, Graphite;        \newline
	    Filebeat, Logstash, Clickhouse (as a storage);\newline
	    Gitlab CI, FPM (for rpms building);           \newline
	    Nginx;\newline
		Hadoop (HDFS, YARN, Hive, Mapred, HBASE);     \newline
		Kerberos;\newline
		Docker, Portainer, Docker Stack;              \newline
		Clickhouse;                                   \newline
		Ansible, Puppet;                              \newline
		Apache Kafka;                                 \newline
		Apache Ignite;\newline
		Apache Spark;\newline
		Jenkins, Airflow;\newline
		Superset, Tableau, Redash.
    }
 \end{itemize}
 


%-----------OTHER-----------------
\section{Courses \& Other Stuff}
  \resumeSubHeadingListStart
    \resumeSubItem{Nand2Tetris}
      {Great and well-known course about how computers really work, Coursera, ENG}
    \resumeSubItem{Implementing web-services in Go, Part 1 \& 2}
      {Great Go programming course by Vasily Romanov, RUS}
    \resumeSubItem{Linux Administrating}
      {Comprehensive Linux administrating course by OTUS, RUS}
    \resumeSubItem{Algorithms and Data Structures}
      {CSC courses taken as a part of self-learning, Stepik, RUS}
    \resumeSubItem{Various Machine Learning Courses}{
        \begin{itemize}[noitemsep,nolistsep]
            \item{\small{Supervised Learning}}
	   	    \item{\small{Mathematics and Python for Data Analysis}}
			\item{\small{etc.}}
	    \end{itemize}}
    \resumeSubItem {Various Hadoop Courses}
      {By EMC, Cloudera, Hortonworks etc.}
  \resumeSubHeadingListEnd
%Hadoop Administration - Level 1 Certification Date Apr 2017 – Present IBM
 %   \item\small{
  % \textbf{Big Data Foundations, Level 2: }{IBM Course\vspace{-2pt}}}
  %  \resumeSubItem {Hadoop Foundations, Level 2}
   %   {IBM Course}
%Hadoop Foundations - Level 2 Certification Date Apr 2017 – Present IBM
%Dell EMC Educated Modern Data Center Certification Date Dec 2016 – Present Dell EMC
%EMC Academic Associate, Information Storage and Management Certification Date Dec 2016 – %P%resent License ZE4RW6SRJ1FEC1JC Dell EMC




%-------------------------------------------
\end{minipage}
\end{document}
